### 2013-02-19 article/paper.tex
more implementation details

In this case, the algorithms were implemented as a SQL stored-procedures only,
using indices and intermediate tables when possible. A Python script was used
to run these stored-procedures and collect the benchmarks. For a storage-engine 
we chose InnoDB, the default engine in MySQL 5.5, as it out-performs MyISM in 
most senarios. \footnote{Sara: can we cite Oracle white papers? 
http://www.oracle.com/partners/en/knowledge-zone/mysql-5-5-innodb-myisam-522945.pdf}
\linebreak
Implementation details:
\begin{itemize}
	\item {\bf Helper Tables} We generated the following helper tables 
		to speed up some algorithms:
		\begin{itemize}
			\item {common-neighbors (id1, id2, neighbor)}
			\item {common-neighbors-count (id1, id2, number of common neighbors)}
			\item {neighbors (id, number of neighbors)}
			\item {topN (id, number of neighbors)}
				This table is simply the top 101 items of the neighbors table.
		\end{itemize}
	\item {\bf Common Neighbors (global)} 
		To find the top N records with most common neighbors, 
		we selected them from the common-neighbors-count table.
	\item {\bf Jaccard's Coefficient (global)} 
		We used the following relation between the cardinality of union and intersection:
		\[{|N(x) \cup N(y)|} = {|N(x)| + |N(y)| - |N(x) \cap N(y)|}\]
		So to calculate the score we used the common-neighbors-count and the neighbors helper tables.
	\item {\bf Adamic/Adar (global)} 
\end{itemize}

>>>>

In this case, the algorithms were implemented as a SQL stored-procedures only,
using indices and intermediate tables when possible. A Python script was used
to run these stored-procedures and collect the benchmarks. For a storage-engine 
we chose InnoDB, the default engine in MySQL 5.5, as it out-performs MyISM in 
most senarios. \footnote{Sara: can we cite Oracle white papers? 
http://www.oracle.com/partners/en/knowledge-zone/mysql-5-5-innodb-myisam-522945.pdf}
\linebreak
Implementation details:
\begin{itemize}
	\item {\bf Helper Tables} We generated the following helper tables 
		to speed up some algorithms:
		\begin{itemize}
			\item {common-neighbors (id1, id2, neighbor)}
			\item {common-neighbors-count (id1, id2, number of common neighbors)}
			\item {neighbors (id, number of neighbors)}
			\item {topN (id, number of neighbors)}
				This table is simply the top 101 items of the neighbors table.
		\end{itemize}
	\item {\bf Common Neighbors (global)} 
		To find the top N records with most common neighbors, 
		we selected them from the common-neighbors-count table.
	\item {\bf Jaccard's Coefficient (global)} 
		We used the following relation between the cardinality of union and intersection:
		\[{|N(x) \cup N(y)|} = {|N(x)| + |N(y)| - |N(x) \cap N(y)|}\]
		So to calculate the score we used the common-neighbors-count and the neighbors helper tables.
	\item {\bf Adamic/Adar (global)} 
		We used the common-neighbors joined with the neighbors helper table.
	\item {\bf Preferential attachment (Global)}
		We used only the topN helper table, because the highest products 
		must be combinations of the nodes with most neighbors.
	\item {\bf Common Neighbors (for node)}
		We used a simple join on the edges table, no helper tables required.
	\item {\bf Jaccard's Coefficient (for node)}
		We used the relation between the cardinality of union and intersection,
		with join of two edges tables, and two neighbors helper tables.
	\item {\bf Adamic/Adar (for node)}
		We used join on the edges table, with the neighbors helper table.
	\item {\bf Preferential attachment (for node)}
		We used the topN helper table, just like in the global version.
	\item {\bf Graph Distance (for node)}
		We used a recursive procedure, starting with a temporary table with all the node's neighbors,
		and on each iteration N we added all the neighbors of nodes in depth N-1. This implementation
		required us to reconfigure MySQL maximum recursion depth.
	\item {\bf Katz (for node)}
		We used a recursive procedure to calculate $|P^l(x,y)|$ for all reachable nodes in depth 3,
		and stored that in a temporary table. We then used that to calculate the score.
	\item {\bf Rooted PageRank (for node)}

\end{itemize}
